Supporting Information

### 2018-04-08 SupportingInformation.Rmd
minor typo fixed

The model-averaged (averaging performed using AIC) lower-tail dependence statistic and the model-averaged (again, AIC based) upper-tail dependence statistics are in Tables \ref{tab_pns_LTdep_AICw} and\ref{tab_pns_UTdep_AICw}, respectively. These values were exclusively positive, thereby
differing from what a normal copula would give (i.e., 0), and answering the second part of question 1 for these data - these data
have greater tail dependence (lower and upper) than would be expected from a normal-copula null hypothesis.

@@

Mean values of our statistics, as well as mean Kendall and Spearman
correlations, were computed across all pairs of sampling locations, and confidence intervals of these means were computed via a
spatial resampling scheme, as described in Methods (Table \ref{tab_pns_resamp}).
Confidence intervals of $\cor_l$","$\cor_u$","$\Ps_l$","$\Ps_u$","$\Dsq_l$","$\Dsq_u$"
always excluded $0$ and mean values were positive, indicating tail dependence.
Confidence intervals of $\cor_l-\cor_u$, $\Ps_l-\Ps_u$ and $\Dsq_u-\Dsq_l$
also all were strictly positive, indicating asymmetry of tail dependence, a feature that data with normal copula
structure do not have, providing further evidence answering the third part of question 1.

@@

Plotting Spearman or Kendall correlations between time series for pairs of locations as a function of great circle distance
between the locations (Figure \ref{fig_pns} A, B) showed the typical decline of correlation with increasing
distance. Plotting $\cor_l$ , $\cor_u$ , $\Ps_l$, and $\Ps_u$ against distances between pairs of locations shows these quantities also appear to decline with distance (Figure \ref{fig_pns} C-F). $\Dsq_u$ and $\Dsq_l$ appear to increase with distance, as expected given
their opposite meaning (Figure \ref{fig_pns} G-H). Plotting $\cor_l - \cor_u$, $\Ps_l - \Ps_u$, and $\Dsq_u - \Dsq_l$ against distance (Figure \ref{fig_pns} I-K) did not show a decline with distance, but did demonstrate visuaally the 
statistical result of Table \ref{tab_pns_resamp} that averages of these 
quantities across all pairs of sampling locations were significantly greater 
than zero, showing asymmetry of tail dependence.

>>>>

The model-averaged (averaging performed using AIC) lower-tail dependence statistic and the model-averaged (again, AIC based) upper-tail dependence statistics are in Tables \ref{tab_pns_LTdep_AICw} and \ref{tab_pns_UTdep_AICw}, respectively. These values were exclusively positive, thereby
differing from what a normal copula would give (i.e., 0), and answering the second part of question 1 for these data - these data
have greater tail dependence (lower and upper) than would be expected from a normal-copula null hypothesis.

@@

Mean values of our statistics, as well as mean Kendall and Spearman
correlations, were computed across all pairs of sampling locations, and confidence intervals of these means were computed via a
spatial resampling scheme, as described in Methods (Table \ref{tab_pns_resamp}).
Confidence intervals of $\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_l$, $\Dsq_u$
always excluded $0$ and mean values were positive, indicating tail dependence.
Confidence intervals of $\cor_l-\cor_u$, $\Ps_l-\Ps_u$ and $\Dsq_u-\Dsq_l$
also all were strictly positive, indicating asymmetry of tail dependence, a feature that data with normal copula
structure do not have, providing further evidence answering the third part of question 1.

@@

Plotting Spearman or Kendall correlations between time series for pairs of locations as a function of great circle distance
between the locations (Figure \ref{fig_pns} A, B) showed the typical decline of correlation with increasing
distance. Plotting $\cor_l$ , $\cor_u$ , $\Ps_l$, and $\Ps_u$ against distances between pairs of locations shows these quantities also appear to decline with distance (Figure \ref{fig_pns} C-F). $\Dsq_u$ and $\Dsq_l$ appear to increase with distance, as expected given
their opposite meaning (Figure \ref{fig_pns} G-H). Plotting $\cor_l - \cor_u$, $\Ps_l - \Ps_u$, and $\Dsq_u - \Dsq_l$ against distance (Figure \ref{fig_pns} I-K) did not show a decline with distance, but did demonstrate visually the 
statistical result of Table \ref{tab_pns_resamp} that averages of these 
quantities across all pairs of sampling locations were significantly greater 
than zero, showing asymmetry of tail dependence.
